---
title: "bs4cards"
author: "Juan Ramirez JR"
date: "3/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bs4cards)
```

## Introduction
"bs4cards" is a package that allows users to add "card" elements to their html document using "Bootstrap:" a CSS library that includes lots of pre-made ui elements for websites. A "Card" is a typically square box that contains information in it, such as a title/heading, text, and some sort of color or shading attached to it. this package is useful for people who want to add a little flair to their HTML documents or add Bootstrap to documents that are eventually intended for the web.  

## Features and Basic Usage  
Let's begin by downloading installing the bs4cards package by running the following:

```{r cars, eval = FALSE}
install.packages("bs4cards")
library(bs4cards)
```

Here are a few use cases of the bs4card package:

```{r, eval = FALSE}
cards(
  data,
  title = NULL,
  text = NULL,
  image = NULL,
  link = NULL,
  footer = NULL,
  header = NULL,
  tags = NULL,
  layout = "label-below",
  width = 3,
  spacing = 2,
  breakpoint = 4,
  label_colour = NULL,
  border_colour = NULL,
  border_width = 1,
  border_radius = 3
)
```


This function creates one single Bootstrap card with a few different parameters which change the appearance of he card on the screen. The attributes, according to the vignette, are as follows:

```{r, eval = FALSE}
data -> Data frame
title -> Title for the card
text -> Text for the card
image -> Path to the card image
link -> URL to link to from title and image
footer -> Card footer
header -> Card header
tags -> Tags to be assigned to each card
layout -> Card layout is a string, defaults to "label-below"
width -> Card width is an integer between 1 and 5
spacing -> Spacing between cards is an integer between 0 and 5
breakpoint -> Number between 1 and 5, controlling label size on horizontal and inset layouts
label_colour -> Colour applied to the card label (if NULL, colour inherits)
border_colour ->  Colour applied to the card border (if NULL, colour inherits)
border_width ->  Width of card border is an integer between 0 and 5
border_radius -> Amount of rounding on card corners is an integer between 0 and 5
```

## Example  
Here are some examples of a few different cards made with bs4cards!

```{r}
  cards(
  data = NULL,
  title = "STYLE 1",
  text = "This is a red and blue card!",
  width = 1,
  spacing = 2,
  breakpoint = 2,
  label_colour = "red",
  border_colour = "blue",
  border_width = 2,
  border_radius = 4
  )
```


```{r}
  cards(
  data = NULL,
  title = "STYLE 2",
  text = "A Little Different This Time",
  footer = "this is a footer",
  header = "this is a header",
  layout = "label-above",
  width = 3,
  spacing = 2,
  breakpoint = 4,
  border_width = 1,
  border_radius = 3,
  border_colour = "yellow"
)
```

```{r}

#example data frame
j = c("Juan", "Ramirez")
juanData = data.frame(j)

  cards(
  data = juanData,
  title = "STYLE 3",
  text = "This one has data and tags!",
  tags = j,
  layout = "label-below",
)
```
